--- 
titulo: "USO DE REDES CONVOLUCIONALES PARA LA ESTMACIÓN DE LA INCERTIDUMBRE MEDIANTE CAMPOS ALEATORIOS"
author: "ALFONSO ANDRÉS TOBAR ARANCIBIA"
grado: "Ingeniero Civil"
fecha: "Junio de 2020"
uni: "UNIVERSIDAD TÉCNICA FEDERICO SANTA MARÍA"
prof_guia: "Marcos Valdebenito"
departamento: "DEPARTAMENTO DE OBRAS CIVILES"
prof_2: "Patricio Bonelli"
prof_3: "Ludwig Stowhas"
mensaje: "Hasta que salió"
ciudad: "Valparaíso"
ind: "CONTENIDO"
ind_fig: "ÍNDICE DE FIGURAS"
ind_tab: "ÍNDICE DE TABLAS"
agradecimientos: |
  `r if(knitr:::is_latex_output()) paste(readLines("preliminares/00-agradecimientos.Rmd"), collapse = '\n  ')`
resumen: |
  `r if(knitr:::is_latex_output()) paste(readLines("preliminares/00-resumen.Rmd"), collapse = '\n  ')`
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("preliminares/00-abstract.Rmd"), collapse = '\n  ')`
site: bookdown::bookdown_site
documentclass: phstylee
classoption:
- 10pt
- twoside
- letterpaper
hyperrefoptions:
- bookmarks=true
- bookmarksnumbered
- colorlinks=true
- linkcolor=black
- citecolor=black
- pdfstartview=FitH
- linktocpage
lot: yes
lof: yes
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
